---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# facereaderconverter

<!-- badges: start -->
<!-- badges: end -->

The goal of facereaderconverter is to convert FaceReader txt files to usable csv files that preserve the timings.

## Installation

You can install the development version of facereaderconverter from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("sgbstats/facereaderconverter")
```
or

``` r
# install.packages("devtools")
devtools::install_github("sgbstats/facereaderconverter")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example,eval = FALSE}
library(facereaderconverter)
convertFRFiles("testdata/testdata_detailed.txt")
#this will convert that file to a csv in the same name and location and apply defult settings
```
The default settings are values are returned as numeric/time objects and the names are `janitor`-style `clean_names` so lower case and spaces are replaced with underscores. When `return_data=FALSE` the metadata from the conversion is returned and when it is set to `TRUE` then the function returns the data itself to allow work. If you want to save the file in another location or under another name then specify the outpath.

```{r example2,eval = FALSE}
library(facereaderconverter)
convertFRDirectory("testdata")
#this will convert all txt files in the directory to a csv in the same name and location and apply defult settings
```

This function takes similar arguments to files function. The new arguments are `recrusive` which when true will look for all files in the whole of the inpath directory. `pattern` which when not null will filter the files to only those matching the regex pattern, e.g., if you only wanted to convert the state files. 